---
title: "Test Semantic Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting FFF Data

```{r libraries, message=FALSE}
library(tseries)
library(vars)
library(dplyr)
library(lubridate)
```

First, I grab all the Federal Fund Futures data from Quandl via the Quandl API. I'm getting data for the 1-, 3- and 6- month futures from January 1, 2009 through to December 1, 2016. I then join them into a single dataframe.

```{r ffff}
#Quandl API keys:
#Quandl("CHRIS/CME_FF6", api_key="_zLhoy4-o4M64Ddp47Sx", start_date="2009-01-01")
#Quandl("CHRIS/CME_FF3", api_key="_zLhoy4-o4M64Ddp47Sx", start_date="2009-01-01")
#Quandl("CHRIS/CME_FF1", api_key="_zLhoy4-o4M64Ddp47Sx", start_date="2009-01-01")

load('fff1.rda')
load('fff3.rda')
load('fff6.rda')

fff <- fff1 %>%
  rename(Settle1 = Settle) %>%
  left_join(fff3, by = 'Date') %>%
  rename(Settle3 = Settle) %>%
  left_join(fff6, by = 'Date') %>%
  rename(Settle6 = Settle)
```

Next I'm pulling in my document vectors, which were generated using a Python script (available in the Other folder). I then do a principal compontent analysis on each set of document vectors. Then I join the PCA vectors with the original vectors and the FFF data and generate lagged variables of the futures data.
```{r docvecs}
load('dmc_docvecs.rda')
load('dmm_docvecs.rda')
load('dbow_docvecs.rda')

dmc_pca <- dmc_docvecs %>%
  select(-Date) %>%
  prcomp() %$% x %>%
  data.frame()

dmm_pca <- dmm_docvecs %>%
  select(-Date) %>%
  prcomp() %$% x %>%
  data.frame()

# dbow_pca <- dbow_docvecs %>%
#   select(-Date) %>%
#   prcomp() %$% x %>%
#   data.frame()

dmc <- dmc_docvecs %>%
  bind_cols(dmc_pca) %>%
  left_join(fff, by = 'Date') %>%
  arrange(Date) %>%
  mutate(deltaSettle1 = Settle1 - lag(Settle1),
         deltaSettle3 = Settle3 - lag(Settle3),
         deltaSettle6 = Settle6 - lag(Settle6))

dmm <- dmm_docvecs %>%
  bind_cols(dmc_pca) %>%
  left_join(fff, by = 'Date') %>%
  arrange(Date) %>%
  mutate(deltaSettle1 = Settle1 - lag(Settle1),
         deltaSettle3 = Settle3 - lag(Settle3),
         deltaSettle6 = Settle6 - lag(Settle6))

# dbow <- dbow_docvecs %>%
#   bind_cols(dbow_pca) %>%
#   left_join(fff, by = 'Date') %>%
#   arrange(Date) %>%
#   mutate(deltaSettle1 = Settle1 - lag(Settle1),
#          deltaSettle3 = Settle3 - lag(Settle3),
#          deltaSettle6 = Settle6 - lag(Settle6))

```
Next, I want to check to see which of my series are unit root:

```{r adf, warning=FALSE}

dmm %>% select(PC1) %>% filter(!is.na(PC1)) %>% unlist() %>% adf.test(k = 1)
dmm %>% select(PC1) %>% filter(!is.na(PC1)) %>% unlist() %>% adf.test(k = 1)

dmm %>% select(Settle6) %>% filter(!is.na(Settle6)) %>% unlist() %>% adf.test(k = 1)
dmm %>% select(Settle3) %>% filter(!is.na(Settle3)) %>% unlist() %>% adf.test(k = 1)
dmm %>% select(Settle1) %>% filter(!is.na(Settle1)) %>% unlist() %>% adf.test(k = 1)

dmm %>% select(deltaSettle6) %>% filter(!is.na(deltaSettle6)) %>% unlist() %>% adf.test(k = 1)
dmm %>% select(deltaSettle3) %>% filter(!is.na(deltaSettle3)) %>% unlist() %>% adf.test(k = 1)
dmm %>% select(deltaSettle1) %>% filter(!is.na(deltaSettle1)) %>% unlist() %>% adf.test(k = 1)

```

So all of the futures series are unit roots. The first difference of the futures and my first principle component are not unit roots.

Next, I'll try regressing all three futures time series on the first lag and the first two principal components of the document vectors.

```{r regression}

dmc_model6 <- lm(data = dmc, formula = deltaSettle6 ~ PC1)
summary(dmc_model6)

dmc_model3 <- lm(data = dmc, formula = deltaSettle3 ~ PC1)
summary(dmc_model3)

dmc_model1 <- lm(data = dmc, formula = deltaSettle1 ~ PC1)
summary(dmc_model1)


dmm_model6 <- lm(data = dmm, formula = deltaSettle6 ~ PC1)
summary(dmc_model6)

dmm_model3 <- lm(data = dmm, formula = deltaSettle3 ~ PC1)
summary(dmc_model3)

dmm_model1 <- lm(data = dmm, formula = deltaSettle1 ~ PC1)
summary(dmc_model3)

```

```{r VAR}

dmc_var1 <- dmc %>%
  select(deltaSettle1, PC1) %>%
  filter(!is.na(deltaSettle1)) %>%
  VAR(p = 1)

dmc_var3 <- dmc %>%
  select(deltaSettle3, PC1) %>%
  filter(!is.na(deltaSettle3)) %>%
  VAR(p = 1)

dmc_var6 <- dmc %>%
  select(deltaSettle6, PC1) %>%
  filter(!is.na(deltaSettle6)) %>%
  VAR(p = 1)

dmm_var1 <- dmm %>%
  select(deltaSettle1, PC1) %>%
  filter(!is.na(deltaSettle1)) %>%
  VAR(p = 1)

dmm_var3 <- dmm %>%
  select(deltaSettle3, PC1) %>%
  filter(!is.na(deltaSettle3)) %>%
  VAR(p = 1)

dmm_var6 <- dmm %>%
  select(deltaSettle6, PC1) %>%
  filter(!is.na(deltaSettle6)) %>%
  VAR(p = 1)

dmc_irf6 <- irf(dmc_var6, impulse = 'PC1', response = 'deltaSettle6')
plot(dmc_irf6)

dmc_irf3 <- irf(dmc_var3, impulse = 'PC1', response = 'deltaSettle3')
plot(dmc_irf3)

dmm_irf6 <- irf(dmm_var6, impulse = 'PC1', response = 'deltaSettle6')
plot(dmm_irf6)

dmm_irf3 <- irf(dmm_var3, impulse = 'PC1', response = 'deltaSettle3')
plot(dmm_irf3)


```

